The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-02-18 main.tex
edits in intro

\section{Introduction} \label{sec:intro}
All modern astronomical research makes use of software in some way.
Astronomy as a field has thus long supported the development of software tools
for astronomical tasks, such as scripts that enable individual scientific
research, software packages for small collaborations, and data reduction
pipelines for survey operations.
Some software packages are, or were, supported by large institutions and are
intended for a wide range of users.
These packages therefore typically provide some level of documentation and user
support or training.
Other packages are developed by individual researchers or research groups and
are then typically used by smaller groups for more domain-specific purposes.
For both packages meant for wider distribution and for scripts specific to
particular research projects, a library that addresses common astronomical tasks
simplifies the software development process.
The users of such a library then also benefit from a community and ecosystem
built around a shared foundation.
The \astropy project has grown to become this community for \python astronomy
software, and the \astropypkg core package is a feature-rich \python library.

@@

\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
programming language that is available under a permissive open-source software license and is free of
charge for all major operating systems. The programming language has become especially popular
in the quantitative sciences, where researchers must simultaneously produce research, perform
data analysis, and develop software. A large part of this success owes itself to the vibrant
community of developers and a continuously-growing ecosystem of tools, web services, and stable
well-developed packages that enable easier collaboration on software development, easier
writing and sharing of software documentation, and continuous testing and validation of
software. While dedicated libraries provide support for array representation and
arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{scipy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high-quality and easy-to-use
packages are available, which can help with tasks that are not specific to astronomy but
might be performed in the course of astronomical research, e.g., interfacing with
databases, or statistical inferences.
More recently, the development and mainstream adoption of package managers such
as Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined
the installation process for many libraries, lowering the barriers to entry.

>>>>

\section{Introduction} \label{sec:intro}
All modern astronomical research makes use of software in some way.
Astronomy as a field has thus long supported the development of software tools
for astronomical tasks, such as scripts that enable individual scientific
research, software packages for small collaborations, and data reduction
pipelines for survey operations.
Some software packages are, or were, supported by large institutions and are
intended for a wide range of users.
These packages therefore typically provide some level of documentation and user
support or training.
Other packages are developed by individual researchers or research groups,
are then typically used by smaller groups for more domain-specific purposes, and 
may have less extensive user support. 
For both packages meant for wider distribution and for scripts specific to
particular research projects, a library that addresses common astronomical tasks
simplifies the software development process by encouraging the reuse of common
functions.  
The users of such a library then also benefit from a community and ecosystem
built around a shared foundation.
The \astropy project has grown to become this community for \python astronomy
software, and the \astropypkg core package has becoming this shared foundation.

@@

\python\footnote{\url{https://www.python.org/}} is an increasingly popular, general-purpose
programming language that is available under a permissive open-source software license and is free of
charge for all major operating systems. The programming language has become especially popular
in the quantitative sciences, where researchers must simultaneously conduct research, perform
data analysis, and develop software. A large part of this success owes itself to the vibrant
community of developers and a continuously-growing ecosystem of tools, web services, and stable
well-developed packages that enable easier collaboration on software development, easier
writing and sharing of software documentation, and continuous testing and validation of
software. While dedicated libraries provide support for array representation and
arithmetic \citep[\package{numpy};][]{numpy}, a wide variety of functions for scientific
computing \citep[\package{scipy};][]{scipy}, and publication-quality plotting
\citep[\package{matplotlib};][]{matplotlib}, tens of thousands of other high-quality and easy-to-use
packages are available, which can help with tasks that are not specific to astronomy but
might be performed in the course of astronomical research, e.g., interfacing with
databases, or statistical inferences.
More recently, the development and mainstream adoption of package managers such
as Anaconda\footnote{\url{https://anaconda.org/}} has significantly streamlined
the installation process for many libraries, lowering the barriers to entry for new users.
